\LARGE \bf Informed sampling by Markov Chain Monte Carlo methods

### 2017-01-30 paper.tex
MTDI

\section{Motivating example---Minimal Time Double Integrator}
We start by considering a simple yet important motion-planning problem

The double integrator is a simple yet im-
portant example that nicely illustrates the phase space. Suppose that a second-
order differential equation is given as q  ̈ = u, in which q and u are chosen from R

\section{Problem definition}
\label{sec:pdef}

\subsection{Minimal Time Double Integrator (MTDI)}
In this paper we demonstrate our approach for the specific case of a double integrator system when the objective function is minimizing the trajectory execution time.

Minimal Time Double Integrator

\subsection{general}

\subsection{double integrator}
Discuss how the informed set looks like

>>>>

\section{Motivating example---Minimal-Time Double Integrator}
We start by considering a simple yet important motion-planning problem---the double integrator.
We are given a one-dimensional point robot  with bounded velocity and bounded acceleration moving amid obstacles. We wish to compute the minimal-time trajectory between two states $x_s, x_g$.
A state in this model is described by 
the position $q \in \R$
and
the velocity $\dot{q}\in \R$ of the position
%each coordinate axis.
The dynamics of the system is described by:
$$
x = (q, \dot{q}); 
\hspace{5mm}
u = \ddot{q}.
$$
Here, the control $u [u_{\text{min}}, u_{\text{max}}]$ is the (bounded) acceleration.

Notice that 
(i)~this is model can be seen as a simplified one-dimensional instance of a robot manipulator with many degrees of freedom and that
(ii)~closed form solutions exist to the 2pBVP for this specific case (as well as the generalized instance)~\cite{HN10}.

Let $T(x_1, x_2)$ denote the minimal time to move the robot from state $x_1$ to $x_2$.
Further, set
$$
T(x) = T(x_s, x) + T(x, x_g).
$$ 
Namely, $T(x)$ is the minimal time to reach the goal from the start subject to passing through the state $x$.

\subsection{Informed set}
Recall that for Euclidean spaces minimizing path length, the informed set is a prolate hyperspheroid.
Moreover, this ellipsoid is defined only be the cost $\hat{c}$ of the current best solution and not by the location of the start and goal.

For the case of a double integrator, this is not the case:
\os{show the explicit math and that it depends on the location of the start and goal}

See Fig.~\ref{fig:informed_1d_di}.
\begin{figure}[tb]
  \centering
  	\includegraphics[height = 4.cm ]{level_set.jpg}
  \caption{
    \captionstyle
  	Level sets for the case of minimal-time double integrator. A point $x = (q, \dot{q})$  denote the position and velocity of the robot while the color at $x$ denotes the cost to reach $x_t$ from $x_s$ subject to passing through the state $x$.
  	}
   	\label{fig:informed_1d_di}
	\vspace{-5.5mm}
\end{figure}
